Understanding the Lomb-Scargle Periodogram

### 2016-12-24 PracticalLombScargle.tex
Add initial discussion of structured windows

\begin{itemize}
  \item Nightly (e.g. ground-based imaging)
  \item Uniform, but with missing data (e.g. Kepler)
\end{itemize}

@@

\begin{itemize}
  \item Peak Width and why it's a poor proxy
  \item False Alarm Probability and why it fails
  \item Baluev method and why it's not enough
  \item Motivation of Bootstrap

\end{itemize}

>>>>

We have seen that for uniform data, the perfect aliasing beyond the Nyquist
frequency is a direct consequence of the symmetry of the Dirac-comb window
function.
For non-uniform observations, such symmetry does not exist, but {\it structure}
in the observing window can lead to partial aliasing of signals in the
data.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig14_LINEAR_window}
  \caption{The power spectrum of the observing window for the data shown
    in \fig{LINEAR_data}. Notice the strong spike in power at a period of
    1 day, and related aliases at $1/n$ days for integer $n$.
    There is also a strong spike at $365$ days, and a noticeable spike at
    $\sim 14$ days. Each of these indicate time intervals that appear often
    in the data.
    \figlabel{LINEAR_window}}
\end{figure}

Let's again consider the data shown in \fig{LINEAR_data}. The window power
spectrum for this in \fig{LINEAR_window} shows some quite distinct features,
and these features have an intuitive interpretation.
Namely, if the window power shows a spike at a period of $p$ days, this means
that an observation at time $t_0$ is likely to be followed by another
observation near a time $t_0 + np$ for integer $n$.

Thus the strong spike at a period of 1 day indicate that observations are
taken near the same time of day: this is typical of a ground-based survey
which observes only at night.
The additional spikes at periods of $1/n$ days (for integer $n$) are aliases
of this same effect.

This window also shows a strong spike at a period of 1 year, indicating that
there was a strong seasonal pattern in the observations.
Finally, there is a noticeable spike at approximately 14 days that is likely
related to patterns in scheduling of observing runs.

Recall that a Fourier spectrum observed through a particular window will reflect
a convolution of the true spectrum and the window spectrum
(cf.\ \fig{random_window}), and so we would expect this structure to be
imprinted on the power spectrum measured from the data.

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{fig15_LINEAR_window_effect}
  \caption{The effect of the window function in \fig{LINEAR_window} on the
    power spectrum in \fig{LINEAR_power}.
    The top panel shows the window power spectrum, and the bottom panel shows
    the observed signal power spectrum.
    Both are plotted as a function of frequency (we earlier saw both of these
    as a function of period; see \fig{LINEAR_window} and \fig{LINEAR_power},
    respectively).
    Viewing these as a function of frequency makes it clear that the structure
    in the window function is imprinted on the observed spectrum: both the
    diurnal structure in the main panel, and the annual structure in the inset
    are apparent in the observed spectrum.
    \figlabel{LINEAR_window_effect}}
\end{figure}

This behavior is illustrated in \fig{LINEAR_window_effect}.
The upper panel shows the window power spectrum as a function of frequency, while lower panel shows the observed signal power spectrum as a function of frequency.
As noted in the discussion of \fig{LINEAR_window}, the window function shows a strong signal at frequencies corresponding to 1 day and 1 year; the latter can be seen in the inset plot.
The power at both these scales is clearly imprinted on the observed power spectrum, as shown in the lower panel and its inset.
This imperfect aliasing is similar to the perfect aliasing seen in regularly-sampled data at the Nyquist frequency; however, in this case the aliasing is
imperfect and the effect fades as you move further from the frequency driving
the signal.

\begin{itemize}
  \item Uniform, but with missing data (e.g. Kepler)
\end{itemize}

@@

\begin{itemize}
  \item Peak Width and why it's a poor proxy
  \item False Alarm Probability and why it fails
  \item Baluev method and why it's not enough
  \item Motivation of Bootstrap
\end{itemize}
